Evaluation metrics

### 2018-08-13 manuscript/supplementary_notes/metrics/metrics.Rmd
update to metric characterisation

---
title: "Metric conformity"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
header-includes:
  - \usepackage{tabularx}
mainfont: DejaVu Sans
---

@@

@@

walkdf(assessments[, ], function(assessment) {
  cat(knitr::knit_child("assessment.Rmd", quiet=TRUE, envir = environment()))
})
```

>>>>

---
title: "Evaluation metrics"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
header-includes:
  - \usepackage{tabularx}
mainfont: DejaVu Sans
---

@@

A trajectory, as defined in our evaluation, is a model with multiple abstractions. The top abstraction is the topology, represented by a milestone network, which contains information about the paths each cell can take from their starting point. More complex abstractions involve the mapping of each cell to a particular branch within this network, and the ordering of each cells within these branches (both represented in the milestone percentages).

When designing metrics to compare trajectories, we therefore

- A good overall metric should capture all these different abstractions, so that the resulting trajectory has the best topology, branch assignment and cellular ordering.
- IndividuSome users are more interested in particular abstractions. For example, the actual

Here we define several metrics

@@

walkdf(assessments, function(assessment) {
  cat(knitr::knit_child("assessment.Rmd", quiet=TRUE, envir = environment()))
})
```
